Lies, versus the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)

### 2018-11-01 GSV-comment-brief.Rmd
tweak comment

---
title: "Lies and the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
output:
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  bookdown::tufte_book2:
    citation_package: natbib
    latex_engine: xelatex
    md_extensions: +raw_attribute
bibliography: bibliography.bib
link-citations: yes

@@

>  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
>  of the number of liars in "coin flip" style experiments. However, their method gives 
>  erroneous confidence intervals. I explain why and describe two better
>  ways to calculate probability distributions.

>>>>

---
title: "Lies, versus the lying liars who tell them: comment on Garbarino, Slonim and Villeval (2018)"
author: "David Hugh-Jones"
date: "`r Sys.Date()`"
output:
  bookdown::tufte_html2: 
    pandoc_args: ['--self-contained']
    keep_intermediates: true
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  bookdown::tufte_book2:
    citation_package: natbib
    latex_engine: xelatex
    md_extensions: +raw_attribute
bibliography: bibliography.bib
link-citations: yes

@@

>  Garbarino, Slonim and Villeval (2018) describe a new method to calculate the probability distribution 
>  of the number of liars in "coin flip" style experiments. I run simulations showing that their method almost always gives 
>  erroneous confidence intervals. I explain why and describe two better
>  ways to calculate probability distributions.
